Reproducible Research: Peer Assessment 1
========================================
  
## Loading and preprocessing the data
We're going to load the data and store it in *rawdata* data.frame:
```{r}
rawdata <- read.csv(unzip("activity.zip"))
```

## What is mean total number of steps taken per day?
For this question we're going to ignore the missing values in the dataset:
```{r}
data <- na.omit(rawdata)
```

Now, lets see the total number of steps taken each day so we need to aggregate data:
```{r}
stepsxday <- aggregate(steps ~ date, data, sum)
```

Then print an histogram of the total number of steps taken each day:
```{r}
hist(stepsxday$steps)
```

Let's see how about **mean** and **median** of total numbers of steps taken per day:

```{r}
mean(stepsxday$steps)
median(stepsxday$steps)
```

## What is the average daily activity pattern?

First of all, we're going to aggregate data by steps and interval:

```{r}
stepsxinterval <- aggregate(steps ~ interval, data, mean)
```

Let's see if there's a pattern with a time series plot:

```{r}
plot(stepsxinterval, type = "l")
```

As you can see, there is a 5-minute interval with maximum value, which is:

```{r}
maxval <- subset(stepsxinterval, steps == max(stepsxinterval$steps))
maxval$interval
```

It seems that at 8:35am is when it reach the maximum steps.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?

## BONUS: what is mean total number of steps taken per day (taking NA as 0)?

I reproduce the first question changig NA values as 0. This is done because of some confussing posts in the forum.

```{r}
data2 <- rawdata
data2[is.na(data2)] <- 0
stepsxday2 <- aggregate(steps ~ date, data2, sum)
hist(stepsxday2$steps)
mean(stepsxday2$steps)
median(stepsxday2$steps)
```