Reproducible Research: Peer Assessment 1
========================================
  
## Loading and preprocessing the data
We're going to load the data and store it in *rawdata* data.frame:
```{r}
rawdata <- read.csv(unzip("activity.zip"))
```

## What is mean total number of steps taken per day?
For this question we're going to ignore the missing values in the dataset:
```{r}
data <- na.omit(rawdata)
```

Now, lets see the total number of steps taken each day so we need to aggregate data:
```{r}
stepsxday <- aggregate(steps ~ date, data, sum)
```

Then print a histogram of the total number of steps taken each day:
```{r}
hist(stepsxday$steps)
```

Let's see what happens with the **mean** and **median** of total numbers of steps taken per day:

```{r}
mean(stepsxday$steps)
median(stepsxday$steps)
```

## What is the average daily activity pattern?
First of all, we're going to aggregate data by steps and interval:

```{r}
stepsxinterval <- aggregate(steps ~ interval, data, mean)
```

Let's see if there's a pattern with a time series plot:

```{r}
plot(stepsxinterval, type = "l")
```

The maximum steps are reached at 8:35 AM:

```{r}
maxval <- subset(stepsxinterval, steps == max(stepsxinterval$steps))
maxval$interval
```

And the average steps are:

```{r}
max(stepsxinterval$steps)
```

## Imputing missing values
Let's take a look on missing values:
```{r}
mv <- sum(is.na(rawdata$steps))
```

There are `r mv` missing values. Let's replace these missing values with the mean of each interval (stored in *stepsxinterval*).

```{r}
data2 <- rawdata
# loop through rawdata
for (i in 1:nrow(rawdata)) {
    # if it's a missing value
    if(is.na(rawdata$steps[i])) {
        # replace it with the mean of this interval
        data2$steps[i] <- subset(stepsxinterval, interval == rawdata$interval[i])$steps
    }
}
```

Let's see a historgram of that new data:
```{r}
stepsxday2 <- aggregate(steps ~ date, data2, sum)
hist(stepsxday2$steps)
mean(stepsxday2$steps)
median(stepsxday2$steps)
```

## Are there differences in activity patterns between weekdays and weekends?
Let's prepare the data adding information about weekdays and weekends:
```{r}
# set locale time to english language
Sys.setlocale("LC_TIME", "English")
# adding daytype variable with "weekend" or "weekday" values
data2$daytype <- as.factor(ifelse(weekdays(as.Date(data2$date)) %in% c("Saturday","Sunday"), "weekend", "weekday"))
```

Now, let's see how the data looks:
```{r}
par(mfrow = c(2,1))
sxi.weekend <- aggregate(steps ~ interval, data2, subset = data2$daytype == "weekend", mean)
sxi.weekday <- aggregate(steps ~ interval, data2, subset = data2$daytype == "weekday", mean)
plot(sxi.weekend, type = "l")
plot(sxi.weekday, type = "l")
```
## BONUS: what is mean total number of steps taken per day (taking NA as 0)?

I reproduce the first question changig NA values as 0. This is done because of some confussing posts in the forum.

```{r}
data3 <- rawdata
data3[is.na(data3)] <- 0
stepsxday3 <- aggregate(steps ~ date, data3, sum)
hist(stepsxday3$steps)
mean(stepsxday3$steps)
median(stepsxday3$steps)
```